The Splashback Radius of Planck-SZ clusters

### 2019-03-13 Paper_v2/RSP_paper_new.tex
make changes bold

\begin{abstract}
We present evidence for the existence of the splashback radius in galaxy
clusters selected using the Sunyaev-Zeldovich effect, {\bf a sample unaffected by
systematics related to cluster finding in the optical wavelength range.} We show
that the deprojected cross-correlation of galaxy clusters found in the Planck
survey with galaxies detected photometrically in the Pan-STARRS survey, shows a
sharp steepening feature (a logarithmic slope steeper than $-3$), which we
associate with the splashback radius. We infer the three-dimensional splashback
radius for the SZ cluster sample to be $r_{\rm sp}=1.85_{-0.30}^{+0.26}$
$\mpch$, where the cluster sample has an average halo mass $M_{\rm
500c}=3.0\times10^{14}\msunh$ at an average redshift of $z=0.18$.  The inferred
value of the splashback radius appears consistent with the expected location
for dark matter halos in the standard cold dark matter paradigm. However, given
the limited precision of our measurements, we cannot conclusively confirm or
rule out the smaller splashback radius measured so far in the literature for
optically selected galaxy clusters. We show that the splashback radius does not
depend upon the galaxy magnitude for galaxies fainter than $M_i-5\log
h=-19.44$, and is present at a consistent location in galaxy populations
divided by color. The presence of the splashback radius in the star-forming
galaxy population could potentially be used to put lower limits on the
quenching timescales for galaxies. We can marginally rule out the contamination
of the star-forming galaxy sample by quenched galaxies, but the results would
need further verification with deeper datasets.

@@

\textbf{To avoid such optical cluster selection effects, there have been some
previous efforts to use X-ray selected cluster samples to look for the
splashback radius using the weak lensing signal \citep{umetsu2017lensing,
contigiani2018weak}}. However stacking issues and the low signal-to-noise
ratio remains a significant hurdle for both of them. \textbf{The use of weak
lensing data in these studies could get around the biased nature of the galaxy
distribution by directly probing the dark matter distribution. Along those
lines,} \citet{chang2017splashback} found evidence for the splashback feature
in the weak lensing signal, but their analysis was again done using optically
selected clusters in the Dark energy survey that suffer from the
afore-mentioned issues.

\textbf{In this work, we explore clusters selected using the SZ effect.} While
the SZ selected clusters can also be susceptible to systematic selection
effects, the scales on which the SZ signal is measured and the cluster
selection is performed is much smaller than the expected location of the
splashback radius (typically $R_{\rm 500c}$). We use this sample to explore the
evidence for the splashback radius in observations.  Due to the low
signal-to-noise ratio of the weak lensing signal, we perform our analysis using
cross-correlation of galaxies with clusters.

\textbf{Dynamical friction is expected to slow down massive subhalos, hosting
galaxies that are orbiting the galaxy cluster \citep{chandrasekhar1943dynamical}.
If a majority of the observed galaxies are hosted by these massive
subhalos, the slow down due to dynamical friction would reduce the apocenters
of their orbits, and in turn, bias the measured splashback radius of the host
cluster \citep{more2016detection, diemer2017sparta}. As dynamical
friction timescales are inversely proportional to the mass of the subhalos,
this effect is stronger for more massive subhalos. Therefore, one expects the
splashback radius to be biased low as measured for more massive subhalos
\citep{adhikari2016observing}.  This bias can be overcome by choosing a faint
enough galaxy sample such that the majority of the galaxies reside in low mass
subhalos, unaffected by dynamical friction.} The SDSS sample used by
\citet{more2016detection} was already deep enough such that biases in the
location of the splashback radius due to dynamical friction effects were
expected to be small. Nevertheless, we use galaxy samples, which are fainter by
$0.5-1$ magnitudes compared to those used by \citet{more2016detection}.

@@

This paper is organized as follows. We introduce the observational
data sets we use in Section~\ref{sec:data}, namely the cluster and the
galaxy catalogs. We describe the methods and analysis procedures we
use in Section~\ref{sec:estimators}. We present and discuss our
results in Section~\ref{sec:Results}. Finally, we summarize our
findings in Section~\ref{sec:Conclusions} and discuss possible future
directions. Throughout the paper, we use a flat $\Lambda$CDM cosmology
with $\Omega_{\rm m}=0.27$ and a dimensionless Hubble parameter of $h=0.7$
to convert redshifts and angles into
cosmological distances. Also, we denote three-dimensional distances by
$r$ and projected distances by $R$.

@@

Therefore the model is described by eight model parameters.
We infer the posterior distributions of those parameters by fitting the model for the two-dimensional correlation
function to the measured two-dimensional correlation signal.
We use the affine invariant Markov Chain Monte Carlo sampler of \citet{goodman2010ensemble} as
implemented in the parallel python package {\it emcee} by
\citet{foreman2013emcee}.
\textbf{We let the parameters $\rho_{\mathrm{s}}$, $\rho_0$ and
$s_{\mathrm{e}}$ vary freely during our fitting procedure. Similar to
\citet{more2016detection} we put flat priors on $\log_{10}(r_{\mathrm{s}})$ and
$\log_{10}(r_{\mathrm{t}})$ but double their ranges to $[0.1,5.0]$ compared to
their work in order to stay conservative. We also use a normal prior with a
central value of $\log_{10}(0.2)$ for $\log_{10}(\alpha)$ as deduced from mass
estimates \citep{gao2008redshift}. To be conservative, we once again double the
scale of the prior to be 1.2 compared to \citet{more2016detection}. For the
parameters $\log_{10}(\beta)$ and $\log_{10}(\gamma)$ we also use
normal priors with central values $\log_{10}(6.0)$ and
$\log_{10}(4.0)$, respectively. The scale of the priors is again
doubled compared to \citet{more2016detection} and set equal to 0.4.}

\textbf{It has been a common concern that the profile in
Equation~\ref{eq:model} introduces a point of minimum slope in the logarithmic
derivative profile simply due to the functional form. However,
\citet{baxter2017halo} used a Bayesian evidence approach to assess that the
data is described significantly better by the general profile in
Equation~\ref{eq:model} (with the splashback feature) rather than by the same
profile with fixed $f_{trans} = 1$ (without splashback feature).  The same
conclusion was made by \citet{umetsu2017lensing} who conducted a similar study
but using weak lensing data.}
%\begin{table*}
%    \centering
%    \caption{Summary of the priors used in the MCMC sampling
%procedure. The MCMC chains are constrained using flat priors or
%normal priors on some of the fitting parameters. This table lists
%the ranges of the flat priors and the central positions as well as
%the scales of the normal priors ( format: center | scale ),
%respectively.}
%    \label{tab:priors}
%    \begin{tabular}{ccccccccc}
%    \hline
%    & $\log_{10}(\rho_{\mathrm{s}})$ & $\log_{10}(\alpha)$ & $\log_{10}%(r_{\mathrm{s}})$ & $\rho_0$ & $s_{\mathrm{e}}$ & $\log_{10}(r_{\mathrm{t}})$ & $\log_{10}(\beta)$ & $\log_{10}(\gamma)$ \\
%    \hline
%    Prior Type & None & Normal & Flat & None & None & Flat & Normal & Normal\\
%    \hline
%    Prior Range & - & $\log_{10}(0.2)| 1.2$ & [0.1,5.0] & - & - & [0.1,5.0] & $%\log_{10}(6.0) | 0.4$ & $\log_{10}(4.0) | 0.4$ \\
%    \hline
%    \end{tabular}
%\end{table*}

\textbf{The location of the splashback radius can be identified in various
ways, e.g., as the radius of the outermost shell in theoretical models of
spherical symmetric collapse \citep{adhikari2014splashback, shi2016outer}, or
using non-spherical shells of density jumps \citep{ mansfield2017splashback},
or the average location of the apocenter of particles falling into the cluster
potential \citet{diemer2017splashback}. Although these definitions have subtle
differences, they all follow the general trend of a decreasing splashback
radius with increasing rate of accretion \citep{diemer2017splashback}.
In this paper, we adopt the convention of
\citet{more2015splashback}, who define the location of the splashback radius
for halos on galaxy cluster scales to be the location of the steepest
logarithmic slope of the radially averaged density profile, due to its ease of
accessibility in data.}

@@

\section{Results}
\label{sec:Results}
The measurements of the two-dimensional cluster-galaxy
cross-correlations are shown as black points with error bars in the
first row of Figure~\ref{fig:all_graphs}. The different columns
correspond to the three different absolute magnitude limits that we
have used to select all the galaxies when calculating the
cross-correlations. The cross-correlation signal is clearly detected
in all three measurements. \textbf{The signal-to-noise ratios of the
three different estimates of the two-dimensional cross-correlation signals
amount to 42.4, 43.3 and 30.9 for the galaxy samples PS 21, PS 21.5 and PS 22,
respectively. For comparison, the detection signal-to-noise ratio in
\citet{more2016detection} was 263, a much higher number due to the size of the
cluster sample used in their study.}

@@

\textbf{We show the two-dimensional posterior distributions for each pair of
parameters for the PS 21.5 sample in Figure~\ref{fig:corner_21.5}. The
posterior distributions for the other datasets show similar degeneracies and
are not included in the paper for brevity.
It is observed that there are some strong degeneracies present between
parameters describing the same part of the model in Equation~\ref{eq:model}
(namely $\rho_{\mathrm{in}}$, $f_{\mathrm{trans}}$ and $\rho_{\mathrm{out}}$).
This is expected since certain combinations of parameter values can
very well result in the same functional shape of the different parts of
the model. This degeneracy also leads to some of the parameters not being
constrained tightly (especially $\rho_s$ and $r_s$ due to their strong degeneracy
with $\alpha$). On the other hand, it is important to note that there is
little-to-no degeneracy present between parameters describing different parts
of the model, which means that the location of the transition region is well
constrained. Therefore, the uncertainties of the individual parameters within
the independent parts of the profile do not directly translate into an
uncertainty in the location of the splashback feature.}

@@

We perform a preliminary comparison of the measurements with
expectations from cold dark matter models. The average halo mass of
the PSZ2 clusters as estimated from the Sunyaev-Zeldovich signal
is $M_{\rm 500c}=3.0\times10^{14}$ $\msunh$. We convert this mass
estimate to $M_{\rm 200m}=6.1\times10^{14}$ $\msunh$ using the average
concentration mass relation of halos \citep{Diemer2015} assuming an NFW profile
\citep{HuKravtsov:2003}. Given the average mass and redshift of our
cluster sample, we calculate the expected splashback radius to be
$2.2$ $\mpch$. We base this estimate on the fitting functions
presented in \citet{more2015splashback}. The splashback radius we
find for the three samples is marginally consistent with this expectation
but on the lower side. Given our large error bars further investigation is
warranted.

@@

\textbf{At face value, this result seems to be at odds with the findings
presented by \citet{baxter2017halo}, who find no splashback feature in the blue
galaxy population. Our independent investigations suggest that the splashback
feature gets less prominent as we cross-correlate the galaxy clusters with
galaxies which are progressively bluer in color. In their paper,
\citet{baxter2017halo} considered the bluest quartile of the galaxy population.
Therefore, it is conceivable that they see no evidence for the splashback
feature in their dataset in the bluest population of galaxies. We would also
like to note that the approach used by \citet{baxter2017halo} used to separate
galaxies into red and blue populations is also fundamentally different from our
approach. While \citet{baxter2017halo} use K-corrected magnitudes from SDSS
relying on the photometric redshifts of galaxies (which could have different
uncertainties for the red and the blue population), we rely on a color cut
which depends upon the redshift of the cluster under consideration. The
differences in our conclusions therefore need to be carefully examined given
these analysis differences.}

@@

Our main findings can be summarized as follows:
\begin{itemize}
\item We detect a clear signature of a steepening feature in the
cross-correlation of Planck SZ clusters with Pan-STARRS
galaxies. The steepest logarithmic slopes that we find in our cross-correlation
signals are steeper than $-3$, and would hence be poorly fit by the
NFW profile. We associate this steepening with the splashback feature.
\item The location of the inferred splashback radius is $r_{\rm
sp}=1.85_{-0.30}^{+0.26}$ $\mpch$, which is marginally consistent 
with expectations from numerical simulations for
halos of an average mass $M_{\rm 500c}=3.0\times10^{14}\msunh$ at an
average redshift of $z=0.18$ in a collision-less dark matter Universe.
However, given the errors further investigation is warranted.
\item We find that the location of the steepest slope does not
strongly depend on the magnitude of the galaxy samples we use, once
we go fainter than $M_i-5\log h=-19.44$.
\item By separately studying the cross-correlation of red and blue
galaxies with the clusters, we present evidence for the presence of
the splashback feature in both populations. The existence of the
splashback radius for the
star forming galaxy population could be of significance for the
models of satellite quenching in galaxy clusters. However, photometric
errors hinder a clean interpretation of the signal.
\end{itemize}

@@

While this work was in preparation, we became aware of a related study
namely, \citet{shin2018des}. Our results are complementary to theirs given
the different data samples and cluster catalogs.

@@

Based on observations obtained with Planck
(http://www.esa.int/Planck), an ESA science mission with instruments
and contributions directly funded by ESA Member States, NASA, and
Canada.  Some of the results in this paper have been derived using
the HEALPix (K.M. Górski et al., 2005, ApJ, 622, p759) package

>>>>

\begin{abstract}
We present evidence for the existence of the splashback radius in galaxy
clusters selected using the Sunyaev-Zeldovich effect, a sample unaffected by
systematics related to cluster finding in the optical wavelength range. We show
that the deprojected cross-correlation of galaxy clusters found in the Planck
survey with galaxies detected photometrically in the Pan-STARRS survey, shows a
sharp steepening feature (a logarithmic slope steeper than $-3$), which we
associate with the splashback radius. We infer the three-dimensional splashback
radius for the SZ cluster sample to be $r_{\rm sp}=1.85_{-0.30}^{+0.26}$
$\mpch$, where the cluster sample has an average halo mass $M_{\rm
500c}=3.0\times10^{14}\msunh$ at an average redshift of $z=0.18$. {\bf The inferred
value of the splashback radius appears marginally consistent with the expected location
for dark matter halos in the standard cold dark matter paradigm}. However, given
the limited precision of our measurements, we cannot conclusively confirm or
rule out the smaller splashback radius measured so far in the literature for
optically selected galaxy clusters. We show that the splashback radius does not
depend upon the galaxy magnitude for galaxies fainter than $M_i-5\log
h=-19.44$, and is present at a consistent location in galaxy populations
divided by color. The presence of the splashback radius in the star-forming
galaxy population could potentially be used to put lower limits on the
quenching timescales for galaxies. We can marginally rule out the contamination
of the star-forming galaxy sample by quenched galaxies, but the results would
need further verification with deeper datasets.

@@

To avoid such optical cluster selection effects, there have been some
previous efforts to use X-ray selected cluster samples to look for the
splashback radius using the weak lensing signal \citep{umetsu2017lensing,
contigiani2018weak}. However stacking issues and the low signal-to-noise
ratio remains a significant hurdle for both of them. The use of weak
lensing data in these studies could get around the biased nature of the galaxy
distribution by directly probing the dark matter distribution. Along those
lines, \citet{chang2017splashback} found evidence for the splashback feature
in the weak lensing signal, but their analysis was again done using optically
selected clusters in the Dark energy survey that suffer from the
afore-mentioned issues.

In this work, we explore clusters selected using the SZ effect. While
the SZ selected clusters can also be susceptible to systematic selection
effects, the scales on which the SZ signal is measured and the cluster
selection is performed is much smaller than the expected location of the
splashback radius (typically $R_{\rm 500c}$). We use this sample to explore the
evidence for the splashback radius in observations.  Due to the low
signal-to-noise ratio of the weak lensing signal, we perform our analysis using
cross-correlation of galaxies with clusters.

Dynamical friction is expected to slow down massive subhalos, hosting
galaxies that are orbiting the galaxy cluster \citep{chandrasekhar1943dynamical}.
If a majority of the observed galaxies are hosted by these massive
subhalos, the slow down due to dynamical friction would reduce the apocenters
of their orbits, and in turn, bias the measured splashback radius of the host
cluster \citep{more2016detection, diemer2017sparta}. As dynamical
friction timescales are inversely proportional to the mass of the subhalos,
this effect is stronger for more massive subhalos. Therefore, one expects the
splashback radius to be biased low as measured for more massive subhalos
\citep{adhikari2016observing}.  This bias can be overcome by choosing a faint
enough galaxy sample such that the majority of the galaxies reside in low mass
subhalos, unaffected by dynamical friction. The SDSS sample used by
\citet{more2016detection} was already deep enough such that biases in the
location of the splashback radius due to dynamical friction effects were
expected to be small. Nevertheless, we use galaxy samples, which are fainter by
$0.5-1$ magnitudes compared to those used by \citet{more2016detection}.

@@

This paper is organized as follows. We introduce the observational
data sets we use in Section~\ref{sec:data}, namely the cluster and the
galaxy catalogs. We describe the methods and analysis procedures we
use in Section~\ref{sec:estimators}. We present and discuss our
results in Section~\ref{sec:Results}. Finally, we summarize our
findings in Section~\ref{sec:Conclusions} and discuss possible future
directions. Throughout the paper, we use a flat $\Lambda$CDM cosmology
with $\Omega_{\rm m}=0.27$ and a dimensionless Hubble parameter of $h=0.7$
to convert redshifts and angles into
cosmological distances. Also, we denote three-dimensional distances by
$r$ and projected distances by $R$. {\bf All distance measurements in this 
paper are given in comoving units.}

@@

Therefore the model is described by eight model parameters.
We infer the posterior distributions of those parameters by fitting the model for the two-dimensional correlation
function to the measured two-dimensional correlation signal.
We use the affine invariant Markov Chain Monte Carlo sampler of \citet{goodman2010ensemble} as
implemented in the parallel python package {\it emcee} by
\citet{foreman2013emcee}.
We let the parameters $\rho_{\mathrm{s}}$, $\rho_0$ and
$s_{\mathrm{e}}$ vary freely during our fitting procedure. Similar to
\citet{more2016detection} we put flat priors on $\log_{10}(r_{\mathrm{s}})$ and
$\log_{10}(r_{\mathrm{t}})$ but double their ranges to $[0.1,5.0]$ compared to
their work in order to stay conservative. We also use a normal prior with a
central value of $\log_{10}(0.2)$ for $\log_{10}(\alpha)$ as deduced from mass
estimates \citep{gao2008redshift}. To be conservative, we once again double the
scale of the prior to be 1.2 compared to \citet{more2016detection}. For the
parameters $\log_{10}(\beta)$ and $\log_{10}(\gamma)$ we also use
normal priors with central values $\log_{10}(6.0)$ and
$\log_{10}(4.0)$, respectively. The scale of the priors is again
doubled compared to \citet{more2016detection} and set equal to 0.4.

It has been a common concern that the profile in
Equation~\ref{eq:model} introduces a point of minimum slope in the logarithmic
derivative profile simply due to the functional form. However,
\citet{baxter2017halo} used a Bayesian evidence approach to assess that the
data is described significantly better by the general profile in
Equation~\ref{eq:model} (with the splashback feature) rather than by the same
profile with fixed $f_{trans} = 1$ (without splashback feature).  The same
conclusion was made by \citet{umetsu2017lensing} who conducted a similar study
but using weak lensing data.
%\begin{table*}
%    \centering
%    \caption{Summary of the priors used in the MCMC sampling
%procedure. The MCMC chains are constrained using flat priors or
%normal priors on some of the fitting parameters. This table lists
%the ranges of the flat priors and the central positions as well as
%the scales of the normal priors ( format: center | scale ),
%respectively.}
%    \label{tab:priors}
%    \begin{tabular}{ccccccccc}
%    \hline
%    & $\log_{10}(\rho_{\mathrm{s}})$ & $\log_{10}(\alpha)$ & $\log_{10}%(r_{\mathrm{s}})$ & $\rho_0$ & $s_{\mathrm{e}}$ & $\log_{10}(r_{\mathrm{t}})$ & $\log_{10}(\beta)$ & $\log_{10}(\gamma)$ \\
%    \hline
%    Prior Type & None & Normal & Flat & None & None & Flat & Normal & Normal\\
%    \hline
%    Prior Range & - & $\log_{10}(0.2)| 1.2$ & [0.1,5.0] & - & - & [0.1,5.0] & $%\log_{10}(6.0) | 0.4$ & $\log_{10}(4.0) | 0.4$ \\
%    \hline
%    \end{tabular}
%\end{table*}

The location of the splashback radius can be identified in various
ways, e.g., as the radius of the outermost shell in theoretical models of
spherical symmetric collapse \citep{adhikari2014splashback, shi2016outer}, or
using non-spherical shells of density jumps \citep{ mansfield2017splashback},
or the average location of the apocenter of particles falling into the cluster
potential \citet{diemer2017splashback}. Although these definitions have subtle
differences, they all follow the general trend of a decreasing splashback
radius with increasing rate of accretion \citep{diemer2017splashback}.
In this paper, we adopt the convention of
\citet{more2015splashback}, who define the location of the splashback radius
for halos on galaxy cluster scales to be the location of the steepest
logarithmic slope of the radially averaged density profile, due to its ease of
accessibility in data.

@@

\section{Results}
\label{sec:Results}
The measurements of the two-dimensional cluster-galaxy
cross-correlations are shown as black points with error bars in the
first row of Figure~\ref{fig:all_graphs}. The different columns
correspond to the three different absolute magnitude limits that we
have used to select all the galaxies when calculating the
cross-correlations. The cross-correlation signal is clearly detected
in all three measurements. The signal-to-noise ratios of the
three different estimates of the two-dimensional cross-correlation signals
amount to 42.4, 43.3 and 30.9 for the galaxy samples PS 21, PS 21.5 and PS 22,
respectively. For comparison, the detection signal-to-noise ratio in
\citet{more2016detection} was 263, a much higher number due to the size of the
cluster sample used in their study.

@@

We show the two-dimensional posterior distributions for each pair of
parameters for the PS 21.5 sample in Figure~\ref{fig:corner_21.5}. The
posterior distributions for the other datasets show similar degeneracies and
are not included in the paper for brevity.
It is observed that there are some strong degeneracies present between
parameters describing the same part of the model in Equation~\ref{eq:model}
(namely $\rho_{\mathrm{in}}$, $f_{\mathrm{trans}}$ and $\rho_{\mathrm{out}}$).
This is expected since certain combinations of parameter values can
very well result in the same functional shape of the different parts of
the model. This degeneracy also leads to some of the parameters not being
constrained tightly (especially $\rho_s$ and $r_s$ due to their strong degeneracy
with $\alpha$). On the other hand, it is important to note that there is
little-to-no degeneracy present between parameters describing different parts
of the model, which means that the location of the transition region is well
constrained. Therefore, the uncertainties of the individual parameters within
the independent parts of the profile do not directly translate into an
uncertainty in the location of the splashback feature.

@@

We perform a preliminary comparison of the measurements with
expectations from cold dark matter models. The average halo mass of
the PSZ2 clusters as estimated from the Sunyaev-Zeldovich signal
is $M_{\rm 500c}=3.0\times10^{14}$ $\msunh$. {\bf We convert this mass
estimate to $M_{\rm 200m}=6.1\times10^{14}$ $\msunh$ using the average
concentration mass relation of halos \citep{Diemer2015} assuming an NFW profile
\citep{HuKravtsov:2003}. Given the average mass and redshift of our
cluster sample, we calculate the expected splashback radius to be
$2.2$ $\mpch$.} We base this estimate on the fitting functions
presented in \citet{more2015splashback}. {\bf The splashback radius we
find for the three samples is marginally consistent with this expectation
but on the lower side. Given our large error bars further investigation is
warranted.}

@@

At face value, this result seems to be at odds with the findings
presented by \citet{baxter2017halo}, who find no splashback feature in the blue
galaxy population. Our independent investigations suggest that the splashback
feature gets less prominent as we cross-correlate the galaxy clusters with
galaxies which are progressively bluer in color. In their paper,
\citet{baxter2017halo} considered the bluest quartile of the galaxy population.
Therefore, it is conceivable that they see no evidence for the splashback
feature in their dataset in the bluest population of galaxies. We would also
like to note that the approach used by \citet{baxter2017halo} used to separate
galaxies into red and blue populations is also fundamentally different from our
approach. While \citet{baxter2017halo} use K-corrected magnitudes from SDSS
relying on the photometric redshifts of galaxies (which could have different
uncertainties for the red and the blue population), we rely on a color cut
which depends upon the redshift of the cluster under consideration. The
differences in our conclusions therefore need to be carefully examined given
these analysis differences.

@@

Our main findings can be summarized as follows:
\begin{itemize}
\item We detect a clear signature of a steepening feature in the
cross-correlation of Planck SZ clusters with Pan-STARRS
galaxies. The steepest logarithmic slopes that we find in our cross-correlation
signals are steeper than $-3$, and would hence be poorly fit by the
NFW profile. We associate this steepening with the splashback feature.
\item {\bf The location of the inferred splashback radius is $r_{\rm
sp}=1.85_{-0.30}^{+0.26}$ $\mpch$, which is marginally consistent 
with expectations from numerical simulations for
halos of an average mass $M_{\rm 500c}=3.0\times10^{14}\msunh$ at an
average redshift of $z=0.18$ in a collision-less dark matter Universe.
However, given the errors further investigation is warranted.}
\item We find that the location of the steepest slope does not
strongly depend on the magnitude of the galaxy samples we use, once
we go fainter than $M_i-5\log h=-19.44$.
\item By separately studying the cross-correlation of red and blue
galaxies with the clusters, we present evidence for the presence of
the splashback feature in both populations. The existence of the
splashback radius for the
star forming galaxy population could be of significance for the
models of satellite quenching in galaxy clusters. However, photometric
errors hinder a clean interpretation of the signal.
\end{itemize}

@@

{\bf While this work was in preparation, we became aware of a related study
by \citet{shin2018des}. Our results are complementary to theirs given
the different data samples and cluster catalogs.}

@@

{\bf Based on observations obtained with Planck
(http://www.esa.int/Planck), an ESA science mission with instruments
and contributions directly funded by ESA Member States, NASA, and
Canada.  Some of the results in this paper have been derived using
the HEALPix package \citep{gorski2005}}
